---
title: "PubH7462_HW1_panxx408"
author: "Mingming Pan"
date: "2/2/2022"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(forcats)
library(dplyr)

```


#### Problem 2.1 Independent Bivariate Normal Random Sample
```{r}
#Create Tibble
set.seed(7462)
Tibble_2.1 <- tibble(x = rnorm(1000, 0, 1),
       y = rnorm(1000, 1, 2),
       sum_indicator = ifelse(x + y >0.5, TRUE, FALSE))
Tibble_2.1 <- Tibble_2.1 %>%
  mutate(sum_indicator_new = as.factor(ifelse(sum_indicator == "TRUE", "Yes", "No"))) 

#Reorder the factor that Yes comes before No
Tibble_2.1$sum_indicator_new <- forcats::fct_relevel(Tibble_2.1$sum_indicator_new,
                                                     "Yes", "No")
```

```{r}
#Scatter plot of Y ~ X
Plot_2.1 <- ggplot(data = Tibble_2.1, aes(x = x, y= y, color = sum_indicator_new)) +
  geom_point() +
  labs(title = "Scatter Plot of Y ~ X", 
       x ="X ~ N(0, 1)", 
       y = "Y ~ N(1, 2)",
       color = "x + y > 0.5") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        legend.position = "bottom" )
Plot_2.1
```
#### Problem2.2 Penguin EDA
```{r}
#read data with relative path
penguin_df <- read_rds("./data/penguin.RDS")
round(mean(penguin_df$flipper_length_mm, na.rm = TRUE), digits = 2)
```

#### Problem 2.2.1 Data Description
+ Penguin data set describes the Size measurements for adult foraging penguins near Palmer Station, Antarctica.
+ There are `r nrow(penguin_df)` rows and `r ncol(penguin_df)` columns
+ Variables are:  **species**: a factor denoting penguin species (Adélie, Chinstrap and Gentoo);**island**: a factor denoting island in Palmer Archipelago, Antarctica (Biscoe, Dream or Torgersen);**bill_length_mm**: a number denoting bill length (millimeters); **bill_depth_mm**: a number denoting bill depth (millimeters); **flipper_length_mm**: an integer denoting flipper length (millimeters); **body_mass_g**: an integer denoting body mass (grams); **sex**: a factor denoting penguin sex (female, male); **year**: an integer denoting the study year (2007, 2008, or 2009).
+ The mean of flipper length is `r round(mean(penguin_df$flipper_length_mm, na.rm = TRUE), digits = 2)`(mm), and the standard deviation is `r round(sd(penguin_df$flipper_length_mm, na.rm = TRUE), digits = 2)`(mm). The mean of bill length is `r round(mean(penguin_df$bill_length_mm, na.rm = TRUE), digits = 2)`(mm) and the standard deviation is `r round(sd(penguin_df$bill_length_mm, na.rm = TRUE), digits = 2)`(mm).

#### Problem2.2.2 Visualization
```{r, warning=FALSE}
#Remove NA of bill length, flipper Length, and sex
penguin_clean <- penguin_df %>%
  filter(!is.na(flipper_length_mm), !is.na(bill_length_mm), !is.na(sex))
#Scatter plot of flipper length ~ bill length 
Plot_2.2 <- ggplot(data = penguin_clean, aes(x = bill_length_mm, y = flipper_length_mm, 
                                          color = species)) +
  geom_point() +
  facet_wrap(vars(sex)) +
  labs(title = "Scatter Plot of Penguin Flipper Length by Bill Length", 
       x = "Bill Length (mm)", 
       y = "Flipper Length (mm)",
       color = "Species") +
  theme(plot.title = element_text(hjust = 0.5 ,size = 20), 
        legend.position = "bottom" )
Plot_2.2
```


Male penguins tend to have larger bill length and larger flipper length than female penguins overall (ignoring the species). 














